Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

A {\em vector addition system (VAS)} in dimension $d$ ($d$-VAS for short) is a $d$-VASS where the set of control-states is a singleton; hence one only needs $T$.\\

@@

	\vspace{-1.2cm}

\alain{il manque des refs dans la fig 1 qui sont déjà dans la biblio: WBTS, omega2,on peut mettre les front lossy avec les LCM et LCS}
%
\section{Resilience for WSTS}

>>>>

A {\em vector addition system (VAS)} in dimension $d$ ($d$-VAS for short) is a $d$-VASS where the set of control-states is a singleton; hence one only needs $T$.

	\vspace{-0.8cm}

% \alain{il manque des refs dans la fig 1 qui sont déjà dans la biblio: WBTS, omega2,on peut mettre les front lossy avec les LCM et LCS}
%

@@

\section{Resilience for WSTS}
